---
title: "Peer-graded Assignment: R Markdown Presentation & Plotly"
author: Surya Praksh Karasala
date: 03/18/2021
autosize: true
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Instructions


Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! Review criteria

The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Loading required package

```{r cars}
library(plotly)
data(iris)
head(iris)
```

## Slide With Plot

```{r}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "SeapalLeangth",
  titlefont = f
)
y <- list(
  title = "PetalLeangth",
  titlefont = f
)
P<-plot_ly(y= iris$Petal.Leangth, x= iris$Sepal.Length,type = "scatter", mode="markers",color=iris$Species)
P <- P %>% layout(xaxis = x, yaxis = y)
P
```

